Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-09-09 bckground.tex
Acknowledgements.

\ifreview
Comments to address in this section:
\begin{itemize}
	\color{red} 
	\item REVIEWER 2: the topic of other HPC usage models [OCCAM,FRHPC],
	elastic simulation jobs [ELASTICMC], opportunistic HPC usage [ATLASHPC]
	or proxy infrastructure [ACTATLAS,ACTHYDRA] is not discussed.\mtnote{I
	looked for these models and found few references to them. All in all, I
	am not seeing how these fit within the background of pilot-enabled
	workload managers.}
\end{itemize}
\fi

>>>>

\ifreview
Comments to address in this section:
\begin{itemize}
	\color{red} 
	\item REVIEWER 2: the topic of other HPC usage models [OCCAM,FRHPC],
	elastic simulation jobs [ELASTICMC], opportunistic HPC usage [ATLASHPC] or
	proxy infrastructure [ACTATLAS,ACTHYDRA] is not discussed.\mtnote{I looked
	for these models and found few references to them. All in all, I am not
	seeing how these fit within the background of pilot-enabled workload
	managers.}\jhanote{As you've exercised diligence in checking, we should
	ignore these suggestions (which are at best advisory, not mandatory)}
\end{itemize}
\fi
